Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2018-07-24 nir_companions.tex
Add Changes as red

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\newcommand*\bl{\color{blue}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Abstract of the paper
\begin{abstract}
    {\bl A}We perform an exploratory study on how to directly detect the near-infrared spectrum of candidate brown dwarf (BD) companions around FGK stars to measure or constrain their masses, thereby asserting their stellar nature or discarding it. {\bl B}We explore two different methods to probe the faint spectra of BD companions. The first technique involves the direct subtraction of two observations shifted to mutually cancel out the spectra of the host star. The second technique applies a \(\chi^{2}\) fit to the individual observations with a synthetic binary model comprised of two PHOENIX-ACES spectra, representing the spectra from the host and companion. The observed spectra are wavelength calibrated and corrected for the atmospheric absorption with the aid of synthetic telluric models.
    {\bl C}The direct subtraction method failed to detect the signature of the companions. The \(\chi^{2}\) technique developed here is able to fit the component for the host star but unable to successfully detect the faint spectra of even the largest companion in our sample. We explore how the companion recovery performs on simulated observations and discuss reasons for the non-detection observed. From the synthetic spectra we determine the upper mass limit for the companions to be around \(\rm 600^{+20}_{-40}~M_{Jup}\) as the limitation of this technique for the data we had on hand. {\bl D}This work highlights the challenges in the spectral detection of faint BD companions. We explore the limitations of the direct subtraction method in the case of small RV separation, and attempt companion recovery at low companion/host flux ratios below 3\%, finding a high upper mass limit from the technique. {\bl This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.}
\end{abstract}

@@

\section{Motivation and target selection}
\label{sec:motivation}
The work of~\citet{sahlmann_search_2011} identified several candidate brown dwarf companions of FGK stars with \(\rm M_2 \sin{i}\) values >\(\rm 10~M_{Jup}\). Seven candidates were selected for observation in order to identify their stellar nature. The target host stars are presented in Table~\ref{tab:starparams} with their stellar parameters, while the companion orbital parameters are provided in Table~\ref{tab:orbitparams}.

>>>>

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\newcommand*\bl{\color{blue}}
\newcommand*\rd{\color{red}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Abstract of the paper
\begin{abstract}
    {\rd A}We perform an exploratory study on how to directly detect the near-infrared spectrum of candidate brown dwarf (BD) companions around FGK stars to measure or constrain their masses, thereby asserting their stellar nature or discarding it. {\rd B}We explore two different methods to probe the faint spectra of BD companions. The first technique involves the direct subtraction of two observations shifted to mutually cancel out the spectra of the host star. The second technique applies a \(\chi^{2}\) fit to the individual observations with a synthetic binary model comprised of two PHOENIX-ACES spectra, representing the spectra from the host and companion. The observed spectra are wavelength calibrated and corrected for the atmospheric absorption with the aid of synthetic telluric models.
    {\rd C}The direct subtraction method failed to detect the signature of the companions. The \(\chi^{2}\) technique developed here is able to fit the component for the host star but unable to successfully detect the faint spectra of even the largest companion in our sample. We explore how the companion recovery performs on simulated observations and discuss reasons for the non-detection observed. From the synthetic spectra we determine the upper mass limit for the companions to be around \(\rm 600^{+20}_{-40}~M_{Jup}\) as the limitation of this technique for the data we had on hand. {\rd D}This work highlights the challenges in the spectral detection of faint BD companions. We explore the limitations of the direct subtraction method in the case of small RV separation, and attempt companion recovery at low companion/host flux ratios below 3\%, finding a high upper mass limit from the technique. {\rd This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.}
\end{abstract}

@@

\section{Motivation and target selection}
\label{sec:motivation}
The work of~\citet{sahlmann_search_2011} identified several candidate brown dwarf companions of FGK stars with \(\rm M_2 \sin{i}\) values >\(\rm 10~M_{Jup}\). Seven candidates {\rd from~\citet{sahlmann_search_2011}} were selected for {\rd further} observation in order to identify their stellar nature. The target host stars are presented in Table~\ref{tab:starparams} with their stellar parameters, while the companion orbital parameters are provided in Table~\ref{tab:orbitparams}.
